\chapter*{Tài liệu Tham khảo}
\addcontentsline{toc}{chapter}{Tài liệu Tham khảo}
\markboth{Tài liệu Tham khảo}{Tài liệu Tham khảo}

\begin{thebibliography}{99}

\bibitem{microsoft2022}
Microsoft Corporation.
\newblock \textit{Microsoft Work Trend Index: Hybrid Work Is Just Work}.
\newblock Microsoft, 2022.
\newblock \url{https://www.microsoft.com/en-us/worklab/work-trend-index}

\bibitem{bain2022whisperx}
M.~Bain, J.~Huh, T.~Han, and A.~Zisserman.
\newblock WhisperX: Time-accurate speech transcription of long-form audio.
\newblock \textit{arXiv preprint arXiv:2303.00747}, 2022.
\newblock \url{https://arxiv.org/abs/2303.00747}

\bibitem{bredin2023pyannote}
H.~Bredin et al.
\newblock pyannote.audio 2.1 speaker diarization: Principle, benchmark, and recipe.
\newblock In \textit{Proceedings of Interspeech 2023}, 2023.
\newblock \url{https://huggingface.co/pyannote/speaker-diarization-3.1}

\bibitem{qwen2025}
Qwen Team.
\newblock \textit{Qwen2.5 Technical Report}.
\newblock Alibaba Cloud, 2024.
\newblock \url{https://arxiv.org/abs/2412.15115}

\bibitem{dettmers2023qlora}
T.~Dettmers, A.~Pagnoni, A.~Holtzman, and L.~Zettlemoyer.
\newblock QLoRA: Efficient finetuning of quantized LLMs.
\newblock In \textit{Advances in Neural Information Processing Systems (NeurIPS)}, 2023.
\newblock \url{https://arxiv.org/abs/2305.14314}

\bibitem{hu2021lora}
E.~J.~Hu, Y.~Shen, P.~Wallis, Z.~Allen-Zhu, Y.~Li, S.~Wang, L.~Wang, and W.~Chen.
\newblock LoRA: Low-rank adaptation of large language models.
\newblock In \textit{International Conference on Learning Representations (ICLR)}, 2022.
\newblock \url{https://arxiv.org/abs/2106.09685}

\bibitem{radford2022whisper}
A.~Radford, J.~W.~Kim, T.~Xu, G.~Brockman, C.~McLeavey, and I.~Sutskever.
\newblock Robust speech recognition via large-scale weak supervision.
\newblock In \textit{International Conference on Machine Learning (ICML)}, 2023.
\newblock \url{https://arxiv.org/abs/2212.04356}

\bibitem{johnson2019faiss}
J.~Johnson, M.~Douze, and H.~Jégou.
\newblock Billion-scale similarity search with GPUs.
\newblock \textit{IEEE Transactions on Big Data}, 7(3):535--547, 2019.
\newblock \url{https://github.com/facebookresearch/faiss}

\bibitem{shankar2022mlops}
V.~Shankar, R.~Garcia, J.~E.~Gonzalez, and J.~Hellerstein.
\newblock Operationalizing machine learning: An interview study.
\newblock \textit{arXiv preprint arXiv:2209.09125}, 2022.
\newblock \url{https://arxiv.org/abs/2209.09125}

\bibitem{ji2023hallucination}
Z.~Ji, N.~Lee, R.~Frieske, T.~Yu, D.~Su, Y.~Xu, E.~Ishii, Y.~Bang, A.~Madotto, and P.~Fung.
\newblock Survey of hallucination in natural language generation.
\newblock \textit{ACM Computing Surveys}, 55(12):1--38, 2023.
\newblock \url{https://arxiv.org/abs/2202.03629}

\bibitem{brown2020gpt3}
T.~B.~Brown et al.
\newblock Language models are few-shot learners.
\newblock In \textit{Advances in Neural Information Processing Systems (NeurIPS)}, 2020.
\newblock \url{https://arxiv.org/abs/2005.14165}

\bibitem{vaswani2017attention}
A.~Vaswani, N.~Shazeer, N.~Parmar, J.~Uszkoreit, L.~Jones, A.~N.~Aiden, Ł.~Kaiser, and I.~Polosukhin.
\newblock Attention is all you need.
\newblock In \textit{Advances in Neural Information Processing Systems (NeurIPS)}, 2017.
\newblock \url{https://arxiv.org/abs/1706.03762}

\bibitem{prometheus2024}
The Prometheus Authors.
\newblock \textit{Prometheus Monitoring System \& Time Series Database}.
\newblock \url{https://prometheus.io}, 2024.

\bibitem{celery2024}
Celery Project.
\newblock \textit{Celery: Distributed Task Queue}.
\newblock \url{https://docs.celeryq.dev}, 2024.

\bibitem{fastapi2024}
S.~Ramírez.
\newblock \textit{FastAPI Framework, high performance, easy to learn, fast to code}.
\newblock \url{https://fastapi.tiangolo.com}, 2024.

\end{thebibliography}
